\section * {Welcome to our course!}
\large

\begin{itemize}
    \item In this course we will be experimenting with and learning about a number of practical techniques and methods to manage and control information such as they are performed in the modern office.
    \item If you work hard and follow all the exercises I instruct you to perform, at the end of this course you will be able to make money using the skills by working in an office either on a full-time basis or through temple work through temporary office agencies.    
    
    This can be quite lucrative and it's something I did myself in the early days while I was looking for the perfect full-time job to start my career.
    
    \item These skills can provide you with financial security to make money when you need to find yourself between To keep you going between your other activities.
    
    \item You will learn how to use Microsoft office including its four major components of 
        \begin{enumerate}
            \item Word processor
            \item Excel spreadsheet to manipulate numbers   
            \item PowerPoint to do presentations   
            \item Access which is a small database that will introduce the concepts of data management with the structured query language SQ   
        \end{enumerate}
    \item 
    
Because the focus in the modern office is on managing tracking controlling and manipulating data you will be learning some advanced skills to do this including Power BI and the use of some basic Python programming including the Pandas and Numpy packages to do the things that SQL and Excel formulas cannot do. \newline

Put these things on your resume and you will have no problem finding a very high paying job within a short period of time after you graduate. \newline

But make sure you learn them because the employer will give you a preemployment test and you will have the opportunity to demonstrate a basic familiarity with the skills. Treat this course as your rehearsal and practice for your first job.
\end{itemize}




